How South Koreans View Democracy?

### 2024-04-18 paper/paper.qmd
updating model

---
title: "How South Koreans View Democracy?"
subtitle: "An Analysis of Survey Data in 2016"
author: 
  - Hailey Jang 
thanks: "Code and data are available at: https://github.com/Hailey-Jang/How_South_Koreans_View_Democracy.git."
date: today
date-format: long
abstract: "This study explores the impact of globalization on democratic values and participation in South Korea by employing a linear regression model to analyze responses from a nationwide questionnaire on citizens' perceptions and engagement. It found that economic disparities and transformative political changes significantly influence citizens’ views on democracy and their participation levels. Through this quantitative analysis, the research uncovers a complex relationship between socio-economic factors and democratic perception, demonstrating how economic inequalities can diminish feelings of representation and reduce democratic participation. These findings underscore the importance of addressing economic and social inequalities to foster a more inclusive and participative democratic environment in South Korea, contributing to our broader understanding of how globalization shapes political systems worldwide."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

This paper delves into the significant question of how economic disparities and political transformations influence the democratic perceptions of South Korean citizens. By examining how global forces reflect in the populace's political engagement and representational sentiments, this study seeks to enrich our understanding of the contemporary democratic ethos in South Korea. To address these inquiries, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens, capturing their perceptions of democracy and their participation in the democratic process. Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions, social contexts, and their democratic engagement. This methodological approach allows for a detailed exploration of how socio-economic factors influence perceptions and behaviours related to democracy in South Korea.

The findings of this study are vital for understanding the current state and future trajectory of democracy in regions undergoing rapid globalization. By highlighting how socio-economic disparities influence democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes. This paper is structured to first introduce the broader context and motivation, followed by an explanation of the data and methods used, presentation of the results, and a discussion that places these findings within the larger theoretical and practical frameworks of democracy and globalization.

@@

As show in @tbl-variables, the dependent variable will be based on the question, "On the whole, are you very satisfied, fairly satisfied, not very satisfied, or not at all satisfied with the way democracy works in South Korea?" The responses are coded on a four-point scale: 1. very satisfied, 2. fairly satisfied, 3. not very satisfied, and 4. not at all satisfied. For the independent variables, key variables on economic satisfaction will include responses to the question, "Would you say that over the past twelve months, the state of the economy in South Korea has gotten much better, gotten somewhat better, stayed about the same, gotten somewhat worse, or gotten much worse?" Answers are coded as 1. Gotten better, 2. stayed the same, 3. gotten worse, 4. don’t know. Additionally, perceptions of corruption will be assessed with the question, "How widespread do you think corruption such as bribe taking is among politicians in South Korea?" Responses are coded as 1. Very widespread, 2. Quite widespread, 3. Not very widespread, 4. It hardly happens at all, 8. Don’t know (Don’t read). Lastly, data on political changes will be obtained from the question regarding the performance of President Geun-hye Park's government: "Now thinking about the performance of the government of Geun-hye Park president in general, how good or bad a job do you think the government of Geun-hye Park president did over the past three years? Has she done a very good job?" Political satisfaction responses are coded as 1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job.

@@

# Create the data frame with the variable summary
variable_summary <- data.frame(
  Types = c("The dependent variable", "The independent variables", "", ""),
  Variables = c("Satisfaction_With_Democracy", "Economic_Perception", "Corruption_Perception", "Political_Perception"),
  Criterion = c(
    "1. Very satisfied, 2. Fairly satisfied, 3. Not very satisfied, 4. Not at all satisfied",
    "1. Gotten better, 2. Stayed the same, 3. Gotten worse, 4. Don’t know",
    "1. Very widespread, 2. Quite widespread, 3. Not very widespread, 4. It hardly happens at all, 8. Don’t know",
    "1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job"
  )
)

kable(variable_summary, booktabs = TRUE, escape = FALSE) %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F, position = "left") %>%
  column_spec(1, width = "3cm") %>%  
  column_spec(2, width = "5cm") %>% 
  column_spec(3, width = "7cm")
```

@@

In the @fig-gender-perceptions , we have a set of three bar graphs, each representing a different type of perception—Corruption, Economic, and Political. The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another color representing female respondents (labelled as '2'). The y-axis shows the average perception score, which likely corresponds to a survey response scale. Each bar's height indicates the average score for that perception type among the respective gender group. For instance, we can infer from the graph that both genders have similar average scores for corruption perception, while there may be slight differences in economic and political perceptions.

@@

# Load the data
analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")

# Convert birth year to age since the data is obtained from 2016 (the survey year)
analysis_data$Age <- 2016 - analysis_data$Age

# Group age into intervals for better visualization
analysis_data$AgeGroup <- cut(analysis_data$Age, breaks=seq(min(analysis_data$Age), max(analysis_data$Age) + 10, by=10), right=FALSE)

analysis_data_long <- pivot_longer(analysis_data, 
                                   cols = c("Economic_Perception", "Corruption_Perception", "Political_Perception"), 
                                   names_to = "Perception_Type", 
                                   values_to = "Perception_Score")

# Plotting Perceptions by Gender
ggplot(analysis_data_long, aes(x = factor(Gender), y = Perception_Score, fill = factor(Gender))) +
  geom_bar(stat = "summary", fun = mean, position = position_dodge()) +
  facet_wrap(~Perception_Type, scales = "free_y") +
  labs(x = "Gender", y = "Average Perception Score") +
  theme_minimal()
```

In the @fig-age-perceptions, the same three types of perceptions are displayed. This time, however, they are categorized by age group, which are shown on the x-axis and range from [19,29] to [79,89]. These age groups are likely in ten-year increments, reflecting a broad categorization of respondents by age. The bars are colour-coded by age group, with each colour corresponding to a different age bracket. Similar to the first graph, the y-axis shows the average perception score. This graph illustrates how perceptions change across different age groups. For example, we can observe trends such as whether younger or older age groups rate economic, corruption, or political perceptions higher or lower on average, which might indicate generational differences in attitudes towards these issues.

@@

# Load the data
analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")

# Plotting Perceptions by Age Group
ggplot(analysis_data_long, aes(x = AgeGroup, y = Perception_Score, fill = AgeGroup)) +
  geom_bar(stat = "summary", fun = mean, position = position_dodge()) +
  facet_wrap(~Perception_Type, scales = "free_y") +
  labs(x = "Age Group", y = "Average Perception Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 55, hjust = 1))  # Rotate the x-axis labels
```

@@

By examining the statistical analysis of @tbl-modelresults, we can explore the impact of economic and political changes on the formation of citizens' perceptions. The results of the two models indicate that perceptions of corruption and economics do not significantly influence the formation of perceptions regarding the realization of democracy. However, it was observed that political satisfaction does have a meaningful effect on the formation of democratic realization perceptions. Considering that political perception has a positive relationship with the perception of democratic realization, it can be interpreted that people who perceive a high level of political satisfaction have a positive perception of the realization of democracy.

@@

## Democracy Perception by Different Variables {#sec-first-point}
@fig-economic-perceptions is a scatter plot overlaid with a linear regression trend line, depicting the relationship between Economic Perception and Satisfaction with Democracy. Each dot represents an individual observation from the dataset, with the horizontal axis (x-axis) representing the level of Economic Perception and the vertical axis (y-axis) indicating the level of Satisfaction with Democracy.

The outcome of the graph suggests that there is a positive association between Economic Perception and Satisfaction with Democracy. As Economic Perception increases, so does Satisfaction with Democracy, at least to some extent according to the data points and the upward trend of the regression line. The strength of this association, however, would need to be quantified with a correlation coefficient or by examining the regression coefficients from a statistical model output.
```{r}
#| label: fig-economic-perceptions
#| fig-cap: Democracy Perceptions by Economic Satisfaction
#| echo: false
#| warning: false

@@

analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")

# Satisfaction_With_Democracy and Economic_Perception
ggplot(analysis_data, aes(x = Economic_Perception, y = Satisfaction_With_Democracy)) +
  geom_point(alpha = 0.6) + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Economic Perception", y = "Satisfaction with Democracy") +
  theme_minimal()
```

@fig-Corruption-perceptions shows a negative trend, indicated by the downward-sloping line, suggesting that as negative view of corruption levels in South Korea increases, Satisfaction with Democracy decreases. This outcome is somewhat expected, as higher perceptions of corruption are often associated with lower satisfaction with government institutions and democratic processes.

```{r}
#| label: fig-Corruption-perceptions
#| fig-cap: Democracy Perceptions by Corruption Perception
#| echo: false
#| warning: false

ggplot(analysis_data, aes(x = Corruption_Perception, y = Satisfaction_With_Democracy)) +
  geom_point(alpha = 0.6) + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Corruption Perception", y = "Satisfaction with Democracy") +
  theme_minimal()
```

In contrast, the @fig-political-perceptions depicts a positive relationship between Political Satisfaction and Satisfaction with Democracy, as shown by the upward-sloping line. This suggests that lower levels of Political satisfaction, which may reflect a more favorable view of the political environment or political performance, are associated with increased Satisfaction with Democracy.

@@

ggplot(analysis_data, aes(x = Political_Perception, y = Satisfaction_With_Democracy)) +
  geom_point(alpha = 0.6) + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Political Perception", y = "Satisfaction with Democracy") +
  theme_minimal()
```

## Democracy Perception

```{r}
#| label: fig-relationship-between-perceptions
#| fig-cap: Democracy Perceptions by All Factors
#| echo: false
#| warning: false

library(ggplot2)
library(dplyr)
library(readr)

analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")

ggplot(analysis_data, aes(x = Economic_Perception, y = Satisfaction_With_Democracy)) +
  geom_point(aes(color = "Economic_Perception")) +
  geom_smooth(method = "lm", aes(color = "Economic_Perception"), se = FALSE) +
  geom_point(aes(x = Political_Perception, color = "Political_Perception")) +
  geom_smooth(method = "lm", aes(x = Political_Perception, color = "Political_Perception"), se = FALSE) +
  geom_point(aes(x = Corruption_Perception, color = "Corruption_Perception")) +
  geom_smooth(method = "lm", aes(x = Corruption_Perception, color = "Corruption_Perception"), se = FALSE) +
  labs(x = "Perception Score", y = "Satisfaction With Democracy", color = "Perception Type") +
  scale_color_manual(values = c("blue", "green", "red")) +
  theme_minimal()
```

@@

This research harnessed the analytical power of regression modeling to delve into how perceptions of economic and political shifts influence democratic sensibilities. It unveils a telling paradox: as dissatisfaction with economic and political conditions heightens, so too does the clamor for a more equitable democracy. Conversely, the heightened perception of corruption in Korea tends to dampen democratic sentiment, revealing a widespread disaffection with the governing structures—echoing themes prevalent in much of the current literature. This study's broader significance lies in its nuanced approach, shifting the lens from broad economic trends and institutional stability to the intricate fabric of individual perceptions. By doing so, it offers a granular view of democratic perceptions, tracing the subtle patterns that emerge from the interplay of personal economic and political experiences.

However, this research is not without its limitations. The regression model successfully identified prevailing perceptual trends within the confines of the data but fell short of illuminating the intricate web of interdependencies among these variables. While the study maps out the landscape of tendencies undergirding the three key variables, it stops short of uncovering the deeper, interwoven connections. As such, the path forward for subsequent inquiries is clear: to unearth the elusive threads that bind these insights into a cohesive narrative, furthering our understanding of the forces that shape democratic participation in the face of societal change.

\appendix

# Appendix {-}

# Additional data details

Other variables in the primary dataset

# Model details {#sec-model-details}

## Posterior predictive check

## Interval

>>>>

---
title: "How South Koreans View Democracy?"
subtitle: "An Analysis of Survey Data in 2016"
author: 
  - Hailey Jang 
thanks: "Code and data are available at: https://github.com/Hailey-Jang/How_South_Koreans_View_Democracy.git."
date: today
date-format: long
abstract: "This study explores the impact of globalization on democratic values in South Korea by employing a linear regression model to analyze responses from a nationwide questionnaire on citizens' perceptions. Through the quantitative analysis, the research uncovers a complex relationship between diverse factors and democratic perception, demonstrating how political dissatisfaction can diminish feelings of representation and reduce democratic participation. These findings underscore the importance of addressing economic and political dissatisfaction to foster a more inclusive and participative democratic environment in South Korea, contributing to our broader understanding of how globalization shapes political systems worldwide."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

This paper delves into the significant question of how economic and political dissatisfaction influence the democratic perceptions of South Korean citizens. By examining how global forces reflect in the populace's political engagement and representational sentiments, this study seeks to enrich our understanding of the contemporary democratic ethos in South Korea. To address these inquiries, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens, capturing their perceptions of economic and political aspects. Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions, political contexts, and their democratic engagement. This methodological approach allows for a detailed exploration of how socio-economic factors influence perceptions and behaviours related to democracy in South Korea.

The findings of this study are vital for understanding the current state and future trajectory of democracy in regions undergoing rapid globalization. By highlighting how socio-economic dissatisfaction influence democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes.

@@

As show in @tbl-variables, the dependent variable will be based on the question, "On the whole, are you very satisfied, fairly satisfied, not very satisfied, or not at all satisfied with the way democracy works in South Korea?" The responses are coded on a four-point scale: 1. very satisfied, 2. fairly satisfied, 3. not very satisfied, and 4. not at all satisfied. For the independent variables, key variables on economic satisfaction will include responses to the question, "Would you say that over the past twelve months, the state of the economy in South Korea has gotten much better, gotten somewhat better, stayed about the same, gotten somewhat worse, or gotten much worse?" Answers are coded as 1. Gotten better, 2. stayed the same, 3. gotten worse, 4. don’t know. Additionally, perceptions of corruption will be assessed with the question, "Most politicians are trustworthy." Responses are coded as 1. Strongly agree, 2. Somewhat agree, 3. Neither, 4. Somewhat disagree, 5. Strongly disagree. Lastly, data on political changes will be obtained from the question regarding the performance of President Geun-hye Park's government in 2016: "Now thinking about the performance of the government of Geun-hye Park president in general, how good or bad a job do you think the government of Geun-hye Park president did over the past three years? Has she done a very good job?" Political satisfaction responses are coded as 1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job.

@@

# Create the data frame with the variable summary
variable_summary <- data.frame(
  Types = c("The dependent variable", "The independent variables", "", ""),
  Variables = c("Dissatisfaction with democracy", "Dissatisfaction with economy", "Distrust level agianst politicians", "Dissatisfaction with politics"),
  Criterion = c(
    "1. Very satisfied, 2. Fairly satisfied, 3. Not very satisfied, 4. Not at all satisfied",
    "1. Gotten better, 2. Stayed the same, 3. Gotten worse, 4. Don’t know",
    "1. Strongly agree, 2. Somewhat agree, 3. Neither, 4. Somewhat disagree, 5. Strongly disagree",
    "1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job"
  )
)

kable(variable_summary, booktabs = TRUE, escape = FALSE) %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F, position = "center") %>%
  column_spec(1, width = "2cm") %>%  
  column_spec(2, width = "5cm") %>% 
  column_spec(3, width = "7cm")
```

@@

In the @fig-gender-perceptions , we have a set of three bar graphs, each representing a different type of distrust level agianst Korean politicians, dissatisfaction of economy and politics. The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another color representing female respondents (labelled as '2'). The y-axis shows the average perception score, which likely corresponds to a survey response scale. Each bar's height indicates the average score for that perception type among the respective gender group. Both genders have similar average scores for economic dissatisfaction, while there may be slight differences in distrust against politicians and political dissatisfaction.

@@

# Load the data
analysis_data <- read_csv("/Users/hailey/Desktop/Democracy_Perception_in_South_Korea/data/analysis_data/analysis_data.csv")

analysis_data_long <- pivot_longer(analysis_data, 
                                   cols = c("Dissatisfaction_with_economy", "Distrust_level_agianst_politicians", "Dissatisfaction_with_politics"), 
                                   names_to = "Perception_Type", 
                                   values_to = "Perception_Score")

short_names <- c("Dissatisfaction_with_economy" = "Eco. Dissat.",
                 "Distrust_level_agianst_politicians" = "Pol. Distrust",
                 "Dissatisfaction_with_politics" = "Pol. Dissat.")

analysis_data_long$Perception_Type <- factor(analysis_data_long$Perception_Type,
                                             levels = names(short_names),
                                             labels = short_names[names(short_names)])

analysis_data_long$Gender <- factor(analysis_data_long$Gender, labels = c("Male", "Female"))

# Plotting Perceptions by Gender
ggplot(analysis_data_long, aes(x = factor(Gender), y = Perception_Score, fill = factor(Gender))) +
  geom_bar(stat = "summary", fun = mean, position = position_dodge()) +
  facet_wrap(~Perception_Type, scales = "free_y") +
  labs(x = "Gender", y = "Average Perception Score") +
  theme_minimal() +
  theme(axis.text.x = element_blank())
```

In the @fig-age-perceptions, the same three types of perceptions are displayed. This time, however, they are categorized by birth year, which are shown on the x-axis and range from 1931 to 1997. The darkness of the bars corresponds to age, with darker shades representing older age groups.The @fig-age-perceptions suggest a view of generational sentiments: while economic and political dissatisfaction remain relatively consistent across age groups, there is a notable divergence when it comes to distrust in politicians. The younger generations who exhibit higher levels of distrust indicates a growing skepticism about political figures among newer generations compared to their older counterparts. This shift could reflect the evolving political landscape and the impact of recent events on the trust levels of different age groups.

@@

library(ggplot2)
library(dplyr)
library(readr)
library(tidyr)

# Load the data
analysis_data <- read_csv("/Users/hailey/Desktop/Democracy_Perception_in_South_Korea/data/analysis_data/analysis_data.csv")

analysis_data_long <- pivot_longer(analysis_data, 
                                   cols = c("Dissatisfaction_with_economy", "Distrust_level_agianst_politicians", "Dissatisfaction_with_politics"), 
                                   names_to = "Perception_Type", 
                                   values_to = "Perception_Score")

short_names <- c("Dissatisfaction_with_economy" = "Eco. Dissat.",
                 "Distrust_level_agianst_politicians" = "Pol. Distrust",
                 "Dissatisfaction_with_politics" = "Pol. Dissat.")

analysis_data_long$Perception_Type <- factor(analysis_data_long$Perception_Type,
                                             levels = names(short_names),
                                             labels = short_names[names(short_names)])

ggplot(analysis_data_long, aes(x = Age, y = Perception_Score, fill = Age)) +
  geom_bar(stat = "summary", fun = mean, position = position_dodge()) +
  facet_wrap(~Perception_Type, scales = "free_y") +
  labs(x = "Age Group", y = "Average Perception Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 55, hjust = 1))
```

@@

By examining the statistical analysis of @tbl-modelresults, we can explore the impact of economic and political satisfaction changes on the formation of citizens' perceptions. The results of the two models indicate that perceptions of corruption and economics do not significantly influence the formation of perceptions regarding the realization of democracy. However, it was observed that political satisfaction does have a meaningful effect on the formation of democratic realization perceptions. Considering that political perception has a positive relationship with the perception of democratic realization, it can be interpreted that people who perceive a high level of political satisfaction have a positive perception of the realization of democracy.

@@

## Democracy Perception by Different Variables {#sec-first-point}
@fig-economic-perceptions is a scatter plot overlaid with a linear regression trend line, depicting the relationship between Economic dissatisfaction and dissatisfaction with Democracy.

The outcome of the graph suggests that there is a positive association between  dissatisfaction with economics and dissatisfaction with democracy, as indicated by the upward slope of the trend line. Points on the graph tend to shift from lighter to darker as they move right, suggesting that increased economic dissatisfaction correlates with a higher dissatisfaction with democracy, particularly as age increases. This could imply that older individuals, who potentially have more experience with economic fluctuations and political systems, might perceive a stronger link between economic and democratic dissatisfaction.

```{r}
#| label: fig-economic-perceptions
#| fig-cap: Democracy Perceptions by Economic Satisfaction
#| echo: false
#| warning: false

@@

# Load the data
analysis_data <- read_csv("/Users/hailey/Desktop/Democracy_Perception_in_South_Korea/data/analysis_data/analysis_data.csv")

ggplot(analysis_data, aes(x = Dissatisfaction_with_economy, y = Dissatisfaction_with_democracy, color = Age)) +
  geom_point(alpha = 0.6) + 
  geom_smooth(method = "lm", se = TRUE, color = "blue") +  
  scale_color_viridis_c(option = "D") +  
  labs(x = "Dissatisfaction with Economics", 
       y = "Dissatisfaction with Democracy", 
       title = "Democracy Perceptions by Economic Satisfaction") +
  theme_minimal() +
  theme(legend.position = "bottom")  
```

@fig-politicians-perceptions shows a correlation between mistrust in politicians and dissatisfaction with democracy, with a gradual upward trend line signifying that as mistrust against politicians increases, so does dissatisfaction with democracy. Notably, the younger age groups (lighter colors) seem to be concentrated at higher levels of mistrust, suggesting that younger individuals may be more inclined to distrust politicians and consequently feel more dissatisfied with democracy.

```{r}
#| label: fig-politicians-perceptions
#| fig-cap: Democracy Perceptions by Corruption Perception
#| echo: false
#| warning: false

ggplot(analysis_data, aes(x = Distrust_level_agianst_politicians, y = Dissatisfaction_with_democracy, color = Age)) +
  geom_point(alpha = 0.6) + 
  geom_smooth(method = "lm", se = TRUE, color = "blue") +  
  scale_color_viridis_c(option = "D") +  
  labs(x = "Mistrust against Politicians", 
       y = "Dissatisfaction with Democracy") +
  theme_minimal() +
  theme(legend.position = "bottom")  
```

The @fig-political-perceptions displays a clear positive correlation between dissatisfaction with politics and dissatisfaction with democracy, indicated by the ascending trend line. As political dissatisfaction increases, so does dissatisfaction with democracy, suggesting that negative feelings towards the political system are closely linked with negative perceptions of democratic governance. The gradient color, representing age groups from older (darker) to younger (lighter), reveals a relatively even distribution across the spectrum of political dissatisfaction, signifying that these sentiments are pervasive across different ages without a visible age-related trend in the data. This indicates a general consensus across generations regarding the relationship between political dissatisfaction and democratic discontent.

@@

ggplot(analysis_data, aes(x = Dissatisfaction_with_politics, y = Dissatisfaction_with_democracy, color = Age)) +
  geom_point(alpha = 0.6) + 
  geom_smooth(method = "lm", se = TRUE, color = "blue") +  
  scale_color_viridis_c(option = "D") +  
  labs(x = "Dissatisfaction with Politics", 
       y = "Dissatisfaction with Democracy") +
  theme_minimal() +
  theme(legend.position = "bottom")  
```
## Democracy Perception
The @fig-slop-comparison illustrates the estimated slopes of three different regression models, each representing the impact of a specific type of dissatisfaction—economic, political, and distrust against politicians—on dissatisfaction with democracy. The plot reveals that all three factors have a positive relationship with dissatisfaction with democracy, as indicated by the fact that all the estimated coefficients are above zero. Economic dissatisfaction has the smallest estimated impact, whereas political dissatisfaction has the highest, with distrust against politicians falling in between. The vertical lines represent the confidence intervals for each estimate, and none of them cross the horizontal line at zero, suggesting that all three relationships are statistically significant. The differences in the lengths of these lines indicate varying degrees of certainty about the estimates, with economic dissatisfaction showing the widest interval, implying the least precision.

```{r}
#| label: fig-slop-comparison
#| fig-cap: Comparison of Slopes from Different Regression Models
#| echo: false
#| warning: false

library(dplyr)
library(broom)

# Assuming analysis_data is already loaded and contains the variables
# Fit separate linear models for each factor
models <- list(
  econ = lm(Dissatisfaction_with_democracy ~ Dissatisfaction_with_economy, data = analysis_data),
  pol = lm(Dissatisfaction_with_democracy ~ Dissatisfaction_with_politics, data = analysis_data),
  trust = lm(Dissatisfaction_with_democracy ~ Distrust_level_agianst_politicians, data = analysis_data)
)

# Extract the coefficients with confidence intervals
model_coefficients <- bind_rows(
  lapply(models, function(model) {
    tidy(model, conf.int = TRUE) %>%
      filter(term != "(Intercept)") # Remove the intercept
  }),
  .id = "model"
)

# Rename the factor levels for better graph labeling
model_coefficients$model <- factor(model_coefficients$model, levels = c("econ", "pol", "trust"),
                                   labels = c("Economic Dissatisfaction", "Political Dissatisfaction", "Distrust Against Politicians"))

# Plot the coefficient for each model
ggplot(model_coefficients, aes(x = model, y = estimate, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Factor", y = "Estimated Slope (Coefficient)") +
  theme_minimal()
```

@@

The study presents an examination of how socio-economic and political dissatisfaction influence the democratic sentiments of South Koreans amidst the multifaceted challenges of globalization. By utilizing linear regression models to parse out the effects of these variables on democratic contentment, it delineates a clear pattern where political dissatisfaction holds the most sway in eroding democratic satisfaction, outpacing the influence of distrust in politicians and economic dissatisfaction. These findings illuminate the critical role of political harmony and economic stability in underpinning the health of a democracy. As South Korea faces the winds of global change, such insights are vital for crafting policies that shore up democratic integrity and public trust.

However, the research is not without limitations. It operates on the assumption that the survey responses accurately reflect the intricate reality of individual perceptions, which may not encapsulate the full spectrum of socio-political nuances. The methodology, while robust, cannot account for unmeasured variables that may confound the relationships explored. Furthermore, the cross-sectional nature of the survey data limits the ability to draw causal inferences. Despite these weaknesses, the study contributes significantly to our understanding of democracy in a rapidly evolving socio-economic landscape. It beckons a call for future research to adopt longitudinal approaches and consider a broader array of variables, thereby enriching the discourse on sustaining democratic values amidst the complexities of the modern world.
